\Large \bf One-Step, Three-Factor Authentication With Custom-Fit, In-Ear EEG

### 2017-02-15 paper.tex
Fixed table 3 error

\begin{table}[h]
\begin{center}
\begin{tabular}{rrrl}
\textbf{P} & \textbf{FAR} & \textbf{FRR} & \textbf{Task}\\
\hline
1 & 0.0 & 0.0 & Listen\\
2 & 0.0 & 0.0 & Breathe\\
3 & 0.0 & 0.0 & Breathe\\
4 & 0.0 & 0.0 & Breathe\\
& 5 0.0 & 0.012 & Breathe\\
6 & 0.0 & 0.0 & Breathe\\
7 & 0.0 & 0.0 & Breathe\\
\end{tabular}
\end{center}
\caption{Best-performing passthought, with FAR and FRR, for each participant, using data from the left ear.}
\label{tab:best}
\end{table}

>>>>

\begin{table}[h]
\begin{center}
\begin{tabular}{rrrl}
\textbf{P} & \textbf{FAR} & \textbf{FRR} & \textbf{Task}\\
\hline
1 & 0.0 & 0.0 & Listen\\
2 & 0.0 & 0.0 & Breathe\\
3 & 0.0 & 0.0 & Breathe\\
4 & 0.0 & 0.0 & Breathe\\
5 & 0.0 & 0.012 & Breathe\\
6 & 0.0 & 0.0 & Breathe\\
7 & 0.0 & 0.0 & Breathe\\
\end{tabular}
\end{center}
\caption{Best-performing passthought, with FAR and FRR, for each participant, using data from the left ear.}
\label{tab:best}
\end{table}
